Negative Types

### 2015-03-22 Univalence/outline.tex
cauchy equiv postulate sym

\documentclass{article}
\usepackage{fullpage}
\begin{document}

@@

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a commutative semiring with $\simeq$ as the underlying equivalence relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g.,
$\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$.

\paragraph*{CauchyEquiv.}

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{amssymb}
\begin{document}

@@

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a commutative semiring with $\simeq$ as the underlying equivalence relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g.,
$\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$. The actual proof says that
0, 1, $+$, and $*$ for a commutative semiring structure under the
equivalence that equates $m$ and $n$ if $\texttt{Fin}~m \simeq \texttt{Fin}~n$.

\paragraph*{CauchyEquiv.} Defines the Cauchy representation of
permutations as
$\texttt{Cauchy}~m~n = \texttt{Vec}~(\texttt{Fin}~m)~n$. The
representation is not tight at this point as it neither enforces that
$m=n$ nor that the elements of the vectors are a permutation of the
set $\{0,\ldots,n-1\}$. This is however a building block for actual
permutations (defined in \texttt{ConcretePermutation}) which enforce
both constraints. For that reason, the Cauchy representation has no
inverse and hence is not a commutative semiring unless one postulates
the following:
\[
\textbf{postulate}~\texttt{sym-iso}~:~\{m~n~:~\mathbb{N}\} \rightarrow
  \texttt{Cauchy}~m~n \rightarrow \texttt{Cauchy}~n~m
\]
